Software Model Checking in Embedded Systems

### 2016-01-03 paper.tex
initial comments

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
%\renewcommand{\baselinestretch}{0.93}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Our reliance on the correct functioning of embedded systems is growing rapidly. Such systems are used in a wide range of applications such as micro-grids, airbag control systems, mobile phones, and high-end television sets. These systems are becoming more and more complex and require multi-core processors with scalable shared memory to meet the increasing computational power demands. The reliability of the embedded (distributed) software is thus a key issue in the system development. State-of-the-art verification methodologies for embedded systems generate test vectors (with constraints), use assertion-based verification and high-level processor model during simulation. However, verification of embedded systems raises additional challenges: meet time and energy constraints, handle concurrent software, platform-dependent software, and legacy designs (usually written in low-level languages). This paper describes challenges, problems, and recent advances to ensure the correctness and the timeliness of embedded systems. Reliability issues in the development of modern micro-grids are considered as a prominent model checking application.
\end{abstract}

@@

Embedded computer systems are used in a variety of sophisticated applications, which range from safety-critical systems such as nuclear reactors and automotive controllers, to entertainment software such as games and graphics animation~\cite{Kopetz11}. Embedded systems are ubiquitous in modern day information systems and are becoming increasingly important in our society, especially in micro-grids, where reliability and carbon emission reduction are of paramount importance. As a consequence, human life has also become more and more dependent on the services provided by this type of system; in particular, success of such system depends on the relevance and quality of service it can provide.

A number of distinctive characteristics might influence the embedded system development and verification process, which include: mass production and static structure, functionality determined by software in read-only memory, multi-core processors with scalable shared memory, and limited amount of energy. Additionally, the increasing computational power and decreasing size and cost of processors is enabling system designers to move more functionalities to software. This leads to difficulties in verifying design correctness since stringent constraints imposed by the hardware ({\it e.g.}, real-time, memory allocation, interrupts, and concurrency) must be considered.

@@

State-of-the-art verification methodologies for embedded systems generate test vectors (with constraints), use assertion-based verification, and high-level processor models during simulation. However, verification of embedded systems raises additional challenges, which include: meet time and energy constraints, handle concurrent software, platform-dependent software, and legacy designs (usually written in low-level languages). Thus, the main challenge for verifying embedded systems relies on improving coverage, where more system's functions are verified, and reducing verification time, {\it i.e.}, pruning the state-space exploration during verification. These aspects are of extreme relevance in micro-grids to ensure reliability, which is a key issue for (smart) cities and consumers.

@@

This position paper tackles three major problems in computer-aided verification for embedded systems: (RP1) providing suitable encodings into the Satisfiability Modulo Theories (SMT) theories to reason accurately and effectively about realistic embedded programs, (RP2) exploiting SMT techniques to leverage bounded model checking of multi-threaded software, and (RP3) proving the correctness and the timeliness of embedded systems, by taking into account stringent constraints imposed by the hardware.

>>>>

\usepackage{color}
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
%\renewcommand{\baselinestretch}{0.93}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Our dependency on the correct functioning of embedded systems is rapidly growing, mainly due to their wide range of applications, such as micro-grids, airbag control, health care, surveillance, mobile devices, and high-end television sets. Their structures are becoming more and more complex and now require multi-core processors with scalable shared memory, in order to meet increasing computational power demands. As a consequence, reliability of embedded (distributed) software becomes a key issue during system development, which must be carefully addressed and assured. Normally, state-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use assertion-based verification and high-level processor model during simulation; however, other additional challenges have been raised: the need for meeting time and energy constraints, handling concurrent software, dealing with platform restrictions, evaluating implementation-structure choices, and supporting legacy designs (usually written in low-level languages). The present paper discuss challenges, problems, and recent advances to ensure correctness and timeliness regarding embedded systems. Reliability issues, in the development of modern micro-grids, are then considered, as a prominent model checking application.
\end{abstract}

@@

Generally, embedded computer systems perform dedicated functions with high degree of reliability. They are used in a variety of sophisticated applications, which range from entertainment software, such as games and graphics animation, to safety-critical systems, such as nuclear reactors and automotive controllers~\cite{Kopetz11}. Embedded systems are ubiquitous, in modern day information systems, and are also becoming increasingly important in our society, especially in micro-grids, where reliability and carbon emission reduction are of paramount importance. As a consequence, human life has also become more and more dependent on the services provided by this type of system; in particular, their success depends both on the provided service relevance and quality.

Indeed, many current embedded systems become interesting solutions only if they can reliably
performs their target tasks, such as unmanned aerial vehicles (UAVs) and medical monitoring systems. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may also cost human-lives, which is unacceptable. In addition, wrong diagnosis or condition-evaluation reports also have the potential to compromise patients' health, with serious consequences.

A number of distinctive characteristics might influence the embedded system development and verification process, which include: mass production and static structure, functionality determined by software in read-only memory, multi-core processors with scalable shared memory, and limited amount of energy. Additionally, the increasing computational power and decreasing size and cost common to computer processors is enabling system designers to move more features to software, which consequently leads to difficulties in verifying design correctness, since stringent constraints imposed by the underlying hardware ({\it e.g.}, real-time, memory allocation, interrupts, and concurrency) must be considered.

@@

State-of-the-art verification methodologies for embedded systems generate test vectors (with constraints), use assertion-based verification, and high-level processor models during simulation; however, embedded system verification also raises additional challenges, such as time and energy constraints, handling of concurrent software, platform restrictions, and legacy designs, which are usually developed in low-level languages. \textcolor{red}{dei uma modificada aqui... deh uma olhada... deixei o antigo comentado abaixo:}\textcolor{green}{In summary, the main challenges regarding the verification of embedded systems lie on improving coverage, where more system's functions are verified, reducing verification time, {\it i.e.}, pruning the state-space exploration during verification, and incorporating system models, which allows specific checks regarding system behavior and not only code correctness. For instance, such aspects are of extreme relevance in micro-grids, in order to ensure reliability, which is a key issue for (smart) cities and consumers}.
%In summary, the main challenge when verifying embedded systems lies on improving coverage, where more system's functions are verified, and reducing verification time, {\it i.e.}, pruning the state-space exploration during verification. These aspects are of extreme relevance in micro-grids to ensure reliability, which is a key issue for (smart) cities and consumers.

@@

This position paper tackles three major problems in computer-aided verification for embedded systems: (RP1) providing suitable encodings into the Satisfiability Modulo Theories (SMT) \textcolor{red}{achar outra palavra aqui?:}theories to reason accurately and effectively about realistic embedded programs, (RP2) exploiting SMT techniques to leverage bounded model checking of multi-threaded software, and (RP3) proving correctness and timeliness of embedded systems, by taking into account stringent constraints imposed by hardware\textcolor{green}{and incorporating knowledge about system purpose and associated features}.
